Running simulations of MultipleContactNeutralMigrat.nlogo

### 2023-05-09 RunSims.Rmd
Add manuscript.md

# Unix default NetLogo installation path (adjust to your needs!):
#
netlogopath <- file.path("/home/leonardo/NetLogo")
modelpath <- file.path(simfolder, "MultipleContactNeutralMigrat.nlogo")
outpath <- file.path(simfolder,"Simulations")

@@

## Lambda = 4

* Initial conditions: migration from the regional community and after the area is filled of individuals, then 60% of the area degraded with regular patches (t= 200 for lambda=4 )

```{r SLOSS_lambda4_simulations_lambda4,echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=TRUE}

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
#
nl@experiment <- experiment(expname="NoSelection_pf06_hps3-61_dd1-3",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "birth-rate-birds" = 4,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.001,
                                             "Video" = "false",
                                             "prob-frag" =  0.6,
                                             "Deforestation-at-time" = 200,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"regular\"",
                                             "birds-behavior" = "\"NoSelection\"",
                                             "replacement-rate" = 0.0
                                             ))

#
# Run 10 times this do not set the run variable for output 
#
# nseeds * number_of_parameters / split = 10 * 300 / 4 - total number of jobs = nseeds * split = 10*4
#

@@

@@

## Old code to plot

>>>>

# Unix default NetLogo installation path (adjust to your needs!):
#
netlogopath <- file.path("/home/leonardo/NetLogo")
modelpath <- file.path(simfolder, "MultipleContactNeutralMigrat.nlogo")
outpath <- file.path("Simulations")

@@

## Lambda = 1-4

* Initial conditions: migration from the regional community and after the area is filled of individuals, then 60% of the area degraded with regular patches (t= 200 for lambda=4 ) 
* Check simulations with Migration0-at-deforestation true or false to take into account that immigration happens at the borders and different kinds of deforestation patterns have different border size e.g. regular > randon block

```{r SLOSS_lambda14_simulations,echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=TRUE}

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
# hps = habitat patch size
# dd = dispersal distance 
# brb = bird rate birds 
nl@experiment <- experiment(expname="NoSelection_pf06_hps3-61_dd1-3_brb1-4",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61)),
                                               "birth-rate-birds" = list(values=c(1.7, 2, 3, 4))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.0001,
                                             "Video" = "false",
                                             "prob-frag" =  0.6,
                                             "Deforestation-at-time" = 200,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"regular\"",
                                             "birds-behavior" = "\"NoSelection\"",
                                             "replacement-rate" = 0.0
                                             ))

#
# Run nseeds=10 times 
#
# Total number of jobs = nseeds * split = 10*4 
# Each job runs parameter input matrix / split = nrow(nl@simdesign@siminput) / split =  300 / 4 
#

@@

## Read Simulations

@@

sloss_sim <- bind_rows(sloss_sim,mdl)
saveRDS(sloss_sim, "Simulations/sloss_sim_ff.rds")

## Exploratory Plots

```{r ExploratoryPlots, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
